[dcpo_demsupport]

### 2020-08-28 paper/dcpo_demsupport.Rmd
clean the chunk names

```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}

@@

```{r visualizedUncertain, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}

@@

@@

```{r visualizedMood, fig.cap= "Effects of Democracy on Change in Mood"}

load(here::here("output", "estimates_clsAPSR.RDS"))
load(here::here("output", "estimates_dcpoMeanAPSR.RDS"))
load(here::here("output", "estimates_dcpoAPSR.RDS"))

@@

```{r visualizedSep, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

>>>>

```{r visualizedMoodAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}

@@

```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}

@@

load(here::here("output", "estimates_dcpoMean.RDS"))

@@

```{r visualizedMoodAPSR, fig.cap= "Effects of Democracy on Change in Mood"}

load(here::here("output", "estimates_clsAPSR.RDS"))
load(here::here("output", "estimates_dcpoMeanAPSR.RDS"))

@@

```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

load(here::here("output", "estimates_dcpoAPSR.RDS"))

df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAPSR[[1]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAPSR[[2]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )
